\huge Tor's Usability for Censorship Circumvention

### 2016-04-18 pets2017-paper/pets2017-paper.tex
Remove a layer of hierarchy in sec:quantitative.

\subsection{Methodology} 
This section details of our quantitative user study, such as the censorship environments we placed our users in, how we recruited our 124 participants, and the procedure for the experiment.

\subsubsection{Setup}
We simulated the same three censorship environments from 
our qualitative user study. Details of the E1, E2, and E3
censorship environments and what configurations are necessary for a 
successful connection can be found in Section~\ref{sec:environments}.

@@

\subsubsection{Recruitment}
We recruited about 20 users for each censorship environment
and interface combination, resulting in a total of 124 users. 
Data analysis considerations deem 20 participants in each 
6 interface version and simulated censorship combination a 
minimum to be able to assume normal distributions and 60 participants
testing each interface is large enough to have adequate effect size.

@@

\subsubsection{Procedure}
The one-hour, multi-participant procedure begins when all participants are sitting at their
respective computers in Xlab. Each computer is equipped with an old or modified version
of Tor Browser, Chrome, Firefox, Internet Explorer,  Chrome, and VLC (for screen recording).
Each computer was assigned one of the 6 conditions in the beginning of the study. Participants
were assigned to the seats at random, effectively being assigned a configuration launcher and
simulated censorship environment combination at random.

@@

\subsubsection{Changes During the Experiment}

>>>>

\subsection{Setup}
We simulated the same three censorship environments from 
our qualitative user study. Details of the E1, E2, and E3
censorship environments and what configurations are necessary for a 
successful connection can be found in Section~\ref{sec:environments}.

@@

\subsection{Recruitment}
We recruited about 20 users for each censorship environment
and interface combination, resulting in a total of 124 users. 
Data analysis considerations deem 20 participants in each 
6 interface version and simulated censorship combination a 
minimum to be able to assume normal distributions and 60 participants
testing each interface is large enough to have adequate effect size.

@@

\subsection{Procedure}
The one-hour, multi-participant procedure begins when all participants are sitting at their
respective computers in Xlab. Each computer is equipped with an old or modified version
of Tor Browser, Chrome, Firefox, Internet Explorer,  Chrome, and VLC (for screen recording).
Each computer was assigned one of the 6 conditions in the beginning of the study. Participants
were assigned to the seats at random, effectively being assigned a configuration launcher and
simulated censorship environment combination at random.

@@

\subsection{Changes During the Experiment}
